MINOS Handover Plots

### 2024-06-12 minos/outcomes/ChildPovReduction_plots.Rmd
Small changes to handovers and ChildPovReduction plotting script

  summary_group <- paste0(summary_group, '_income_quint2')

@@

```{r}
scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
#scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
```

>>>>

@@

```{r}
#scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
#scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
scen.list.test <- c('baseline', 'ChildPovertyReductionSUSTAIN')
whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
```

### 2024-06-12 minos/validation/handovers.Rmd
Additions and WIP plots for childPovReduction scripts
Small changes to handovers and ChildPovReduction plotting script

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

@@

@@

#### Absolute
```{r}
raw.2010 <- raw.dat %>%
  filter(time == 2010)

abs.threshold <- weighted.median(x = raw.2010$hh_income, 
                                 w = raw.2010$weight, 
                                 na.rm = TRUE)
abs.threshold <- abs.threshold * 0.6

print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
```

>>>>

```{r}
# Read raw datafiles in
#raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

@@

spaghetti_plot(base.inc, 'hh_income',
               save = shall.we.save,
               save.path = save.path)

@@

#### Absolute
```{r}
# raw.2010 <- raw.dat %>%
#   filter(time == 2010)
# 
# abs.threshold <- weighted.median(x = raw.2010$hh_income, 
#                                  w = raw.2010$weight, 
#                                  na.rm = TRUE)
# abs.threshold <- abs.threshold * 0.6
# 
# print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
```
